---
title: "Three Parameters"
tutorial:
  id: "08-three-parameters"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 8 tutorial"
---

```{r setup, include=FALSE}
library(tidyverse)
library(PPBDS.data)
library(learnr)
library(shiny)
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
options(tutorial.storage="local")  
```

## Confirm Correct Package Version
###

Confirm that you have the correct version of PPBDS.data installed by pressing "Run Code."

```{r confirm, exercise=TRUE}
packageVersion('PPBDS.data')
```

The answer should be ‘0.3.2.9007’, or a higher number. If it is not, you should upgrade your installation by issuing these commands:


```{r confirm-advice, echo=TRUE, eval=FALSE}
remove.packages('PPBDS.data')  
library(remotes)  
remotes::install_github('davidkane9/PPBDS.data')  
```

Strictly speaking, it should not be necessary to remove a package. Just installing it again should overwrite the current version. But weird things sometimes happen, so removing first is the safest approach. 

## Name

```{r name, echo=FALSE}
question_text(
  "Student Name:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

## Submit

```{r context="setup"}
submission_ui
```

```{r context="server"}
submission_server()
```
