---
title: "Tools"
tutorial:
  id: "tools"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Tools Tutorial"
---

```{r setup, include=FALSE}
library(tidyverse)
library(PPBDS.data)
library(learnr)
library(shiny)
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
options(tutorial.exercise.timelimit = 60, tutorial.storage="local")
```


<!-- 4) Should we do more, something with Github? Something with a PDF file? That would certainly get students going to the first set of Study Halls! -->


## Introduction

Open up RStudio on your computer. Then open up the Terminal tab on the left window right next to "Console". This is where we will be running the code for this tutorial's exercises. Before we start, we need to check that Git has been installed first. 

###

### Exercise 1
Copy/paste `git --version`  into the terminal and press return.

###

You should get an output of the git version (ex. git version 2.24.3). If you do not, go to the [Tools](https://davidkane9.github.io/PPBDS/tools.html) section of the primer and follow the directions for installing git.


## Name 


``` {r name}
question_text(
  "Student Name:",
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Modify your answer",
  incorrect = "Ok"
)
```

## Email

``` {r email}
question_text(
  "Email:",
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Modify your answer",
  incorrect = "Ok"
)
```

## The Terminal
###
### Exercise 1

**Working Directory: `pwd`**

First, we need to figure out where we are. To see your current folder, type `pwd` (previews working directory). Hit return, and paste both the line on which you typed the command and the line(s) below it

```{r pwd, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```

###

### Exercise 2

**Seeing Items in the Directory: `ls`**

Type `ls` in the terminal and hit return to see all the items that are located in the bottom right window under "Home". Paste both the line on which you typed the command and the line(s) below it

```{r ls, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```

### Exercise 3 (part I)

**Changing Directories:`cd`**

We will be opening or "changing" into our Desktop directory now. Type in the command `cd Desktop/`. Paste both the line on which you typed the command and the line(s) below it.

```{r cd, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)

```

### Exercise 3 (part II)
Awesome. Now type `ls`. Copy/paste both the line on which you typed the command and the line(s) below it.

```{r cd2, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)

```

### Exercise 4

**Make/Remove Directories: `mkdir`, `rmdir`**

Let's try making a folder called Gov-50. Use the command `mkdir Gov-50`and hit return. Now type `ls` to see your newly created folder! Copy/paste both the line on which you typed the command and the line(s) below it.
 
```{r mk-1, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)

```

### Exercise 5

**Creating files: `touch`**

Now we are going to create a file. Type in `touch: text.txt`and hit return. Now type `ls`. Paste both the line on which you typed the command and the line(s) below it

```{r touch, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)

```

### Exercise 6

**Moving Files: `mv`**

Now try moving our text.txt file to our Gov-50 folder. Type `mv test.txt Gov-50/`. Now let's check! Use `cd` to open our Gov-50 folder and `ls` to show its contents. Paste both the line on which you typed the command and the line(s) below it

```{r mv, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```

### Exercise 7

**Copying Files: `cp`**

Try copying the test.txt file into your Gov-50 folder. Use `cp test.txt Gov-50/`. Paste both the line on which you typed the command and the line(s) below it.

```{r cp-1, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```

### Exercise 8

**Removing Files:`rm`**

Now lets try removing that same text.txt file with `rm`. Use `ls` to make sure it is gone!

## Git
### 

### Exercise 1 

Type `git config user.name`. Copy/paste both the line on which you typed the command and the line(s) below it. 

```{r gc-1, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```


### Exercise 2

Type `git config user.email` .Copy/paste both the line on which you typed the command and the line(s) below it.

```{r gc-2, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```

### Exercise 3

Now, switch out of the terminal window into the console window. Install the package `usethis`. Issue the command `install.packages("usethis")`.

**DO NOT** go on until you have done this.

### Exercise 4

So now that you installed `usethis`, run the command `git_sitrep()`. You will see a bunch of code divided into 5 sections. Copy/paste the first section under **Git config (global)**.

```{r gc-3, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```


### Exercise 5

Awesome. Now copy/paste the third section under **GitHub**.

```{r gc-4, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```

## Submit

Some of these exercises were taken from the collection of [RStudio Primers](https://rstudio.cloud/learn/primers), a great resource for practicing your skills.

```{r context="setup"}
submission_ui
```

```{r context="server"}
submission_server()
```


